BIP-Predictor

### 2025-08-15 Sweave/BIP_predictor.Rnw
up

# We can select type of VAR model
#VAR_type="BVAR"
VAR_type="VAR"
#VAR_type="elastic_net"
if (VAR_type=="BVAR")
{
# Simon's settings for BVAR(4)  
  lambda_BVAR <- 1.001
  p<-3
  q<-0
}
if (VAR_type=="VAR")
{
# Marc's settings for VAR  
  p<-1
  q<-0
}
if (VAR_type=="elastic_net")
{
# Marc's settings for EN
  q<-0
# 1. Simpler (but possibly too simple)  
  p<-2
  nsteps<-5
# 2. Simpler than Simon's original settings (below) but slightly more complex than above ones  (good compromise)
  p<-3
  nsteps<-6
# Simon's original settings (lead to overfitting)  
#  p<-4
#  nsteps<-7
}

>>>>

# We can select type of VAR model
# This is the setting used in the paper
VAR_type="VAR"
#VAR_type="BVAR"
#VAR_type="elastic_net"
if (VAR_type=="BVAR")
{
# Simon's settings for BVAR(4)  
  lambda_BVAR <- 1.001
  p<-3
  q<-0
}
if (VAR_type=="VAR")
{
# Marc's settings for VAR  
  p<-1
  q<-0
}
if (VAR_type=="elastic_net")
{
# Marc's settings for EN
  q<-0
# 1. Simpler (but possibly too simple)  
  p<-2
  nsteps<-5
# 2. Simpler than Simon's original settings (below) but slightly more complex than above ones  (good compromise)
  p<-3
  nsteps<-6
# Simon's original settings (lead to overfitting)  
#  p<-4
#  nsteps<-7
}
